Trauma treatment delay

### 2023-11-24 manuscriptlongversion.Rmd
text

In this study, one of the limitations was the amount of people having
the recorded outcome being quite small, leading to having the variables
being split up into two groups for the logistical regression.
Furthermore, the original plan was to divide RR, SBP and GCS into
revised trauma score (RTS) categories, from 1-4. However, many of the
RTS variables had few to no patients with the observed outcome. This led
to separation in the logistical regression in these variables, referring
to when an outcome variable separates a predictor variable completely,
which occurs when the predictor is only associated with one outcome
value. In the case it was RTS 3 and 4, which left RTS 1 and 2 with
confidence intervalls of 0.00 to infinity.

Discuss limitations of the study, taking into account sources of
potential bias or imprecision. Discuss both direction and magnitude of
any potential bias

>>>>

In this study, one of the limitations was the amount of people having
the recorded outcome being quite small, leading to having the variables
being split up into two groups for the logistical regression.
Furthermore, the original plan was to divide RR, SBP and GCS into
revised trauma score (RTS) categories, from 1-4. However, many of the
RTS variables had few to no patients with the observed outcome. This led
to separation in the logistical regression in these variables, referring
to when an outcome variable separates a predictor variable completely,
which occurs when the predictor is only associated with one outcome
value [@OARC]. In the case of these variables, it was only RTS 3 and 4
who had patients with the observed outcome, which left RTS 1 and 2 with
confidence intervals of 0.00 to infinity. This way would have been the
best way to examine these variables, but as that wasn't possible with
this group of patients, we resorted to making these variables
continuous.

The biases that might have been present in this study would be selection
bias and misclassification bias.
